Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-20 tex/v3/section_5_numeric_expes.tex
new appendix

\subsection{Analysing on toy problem}
We compare \emph{Screenkhorn} to Sinkhorn as implemented in Python Optimal Transport toolbox\footnote{see \url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example. The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means. We consider an unsupervised domain adaptation using optimal transport with entropic regularization.  Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$ and finally, whether the cost matrix $C$ is normalized or not.

@@

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-6}$, when the
number of iterations of number of objective function evaluations reach $10^{5}$. For all
applications, we have set $\eta=1$.

@@

\begin{figure*}[t]
	\centering
%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:wda}
\end{figure*}
\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

>>>>

\subsection{Analysing on toy problem}

@@

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-9}$, when the
number of iterations of number of objective function evaluations reach $10^{6}$. For all
applications, we have set $\eta=1$.

@@

\begin{figure*}[t]
	\centering
%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
   \includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:wda}
\end{figure*}
\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl1.pdf}
	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}
